Proposed Solution

### 2016-11-11 Ennan-Proposal/prelim.tex
stuff

Based on our own experience with misconfigurations,
we have proposed and developed a simple tool for verification of 
configuration files, named
ConfigC~\cite{santolucitoCAV}. Motivated by promising preliminary
results, which we obtained with ConfigC, we believe that automated 
verification of configuration files, before they
are deployed and installed, is possible and that it should be further studied.

From ConfigC we drew the main inspiration for this proposal. In particular, 
ConfigC is a framework that first automatically
analyzes datasets of correct configuration files, 
and then derives rules for building a language model 
from the given datasets.
Finally, the resulting language model could be used to verify 
new configuration files (called target configuration files) and 
detect errors in these target configuration files.
The configuration errors ConfigC can deal with cover:
entry missing errors, ordering errors, type errors and
value correlation.
To our knowledge, there is no existing effort that is able to detect
the above errors, because they are very tricky to identify in
practice.

>>>>

Based on our own experience with misconfigurations,
we have proposed and developed a simple tool for verification of 
configuration files, named
ConfigC~\cite{santolucitoCAV}. Motivated by promising preliminary
results, which we obtained with ConfigC, we believe that automated 
verification of configuration files is possible and that it should be further studied.

From ConfigC we drew the main inspiration for this proposal. We now briefly
outline how does ConfigC work. It first automatically
analyzes datasets of correct configuration files, 
and then derives rules for building a language model 
from the given datasets.

The algorithm can be summarized as follows: we identified several basic types, 
such Boolean, Integer, File. With each of these files we associated a list 
of templates. We then analyze {\emph {correct}} configuration files. When we 
detect that a certain variable (or a pair of variable

\begin{figure}
	\centering
\begin{minipage}{0.9\textwidth}
\begin{parcolumns}{2}
\colchunk{\begin{lstlisting}[language=C, frame=tb, xleftmargin=.01\textwidth]
File 1:
max_connections=300
general_log=1
...
mysql.max_persistent=200
\end{lstlisting}}

\colchunk{\begin{lstlisting}[language=C, frame=tb, xleftmargin=.01\textwidth]
File 2:
max_connections=400
general_log=0
...
mysql.max_persistent=200
\end{lstlisting}}

\colplacechunks
\end{parcolumns}
\end{minipage}
	\caption{Fragments of two configuration files for configuring PHP on MySQL}
\end{figure}

The resulting language model, together with accompanying rules, 
is then used to detect errors in new configuration files.
ConfigC can detect the following errors in configuration files:
entry missing errors, ordering errors, type errors and
simple value correlation. Running ConfigC on Example~1 from 
Sec.~\ref{sec:intro-examples} returns the following output:
\begin{lstlisting}[language=C, xleftmargin=.01\textwidth]
ORDERING ERROR: Expected extension "recode.so" BEFORE 
extension "mysql.so"
\end{lstlisting} 
ConfigC could not detect an error present in Example~2 since it can detect 
only simple comparison-based relations.

To our knowledge, there is no existing effort that is able to detect
the above errors, because they are very tricky to identify in
practice.
